Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2021-05-16 2021/emnlp/auto_cl_mdmt.tex
added comment on parameterization

This problem is often approached by \emph{static} instance selection or re-weighting strategies, where the available training data is used in proportion to its relevance for the chosen test conditions \citep{Moore10selection,Axelrod11domain}. Finding the optimal balance of training data is, however, a challenging task due, for instance, to the similarity between domains/languages, but also due to regularization effects of out-of-domain data \citep{Miceli-barone17regularization}. It may also be suboptimal, as some target domains or languages might be easier to train than others. For example, improving the performance of the MT system in one domain will often hurt that of another \citep{Vanderwees17dynamic, Britz17mixing}, and improving model generalization across all domains \citep{koehn18findings} may not achieve optimally for any particular domain.

Several recent proposals
% \citep{Vanderwees17dynamic,Graves17automated,platanios19competence,Zhang19curriculum,Kumar19reinforcement,Wang20learning-multi,Wang20balancing,Wang20learning-multi}
have explored ways to instead consider \emph{dynamic} data selection and sampling strategies that surpass static strategies. Notably, \citet{Vanderwees17dynamic,Zhang19curriculum} construct a static curriculum, while \citet{Graves17automated,Platanios19competence,Kumar19reinforcement,Wang20balancing,Wang20learning-multi} build curricula that automatically adapt to the training data.

@@

The main challenge is then to make the best of this heterogeneous data, with the aim to achieve the optimal performance for the intended test conditions. These might correspond to data from just one of the training domains, as in standard supervised (multi-source) domain adaptation; a more difficult case is when the test data is from one domain unseen in training (unsupervised domain adaptation); in multi-domain adaptation finally, the test distribution is itself a mixture of domains, some of which may also be observed in training.  Without loss of generality, one may then assume that the test distribution takes the form $\mathcal{D}^{t}(x) = \sum_d \lambda^{t}(d) \mathcal{D}_d(x)$ - with only one non-null  component in the case of pure domain adaptation. These settings are illustrated Figure~\ref{fig:mdmt-lambdas}.
\begin{figure}[h]
  \centering
  \includegraphics[width=0.48\textwidth]{mdmt-lambdas}
  \caption{Training and testing with distribution mismatch. We consider just three domains, and represent vectors of mixture weights $\vlambda^{s}$ and $\vlambda^{t}$ in the 3-dimensional simplex. Training with weights in (a) and testing with weights in (c) is supervised multi-source domain adaptation to domain~2 ($d_2$), while (b)-(c) is the unsupervised version, with no training data from $d_2$; training with weights in (a) and testing with weights in (d) is multi-domain learning, also illustrated with configurations (a)-(e) (training domain $d_1$ is not seen in test), and (b)-(d)  (test domain $d_2$ is unseen in training).}\label{fig:mdmt-lambdas}
\end{figure}

@@

\section{Experimental settings} \label{sec:exp}
\subsection{Data and metrics \label{ssec:corpora}}
We experiment with translation from English into French and use texts initially originating from 6~domains, corresponding to the following data sources: the UFAL Medical corpus V1.0 (\domain{med})\footnote{\url{https://ufal.mff.cuni.cz/ufal_medical_corpus}. We only use the in-domain (medical) subcorpora: PATR, EMEA, CESTA, ECDC.}; the European Central Bank corpus (\domain{bank}) \citep{Tiedemann12parallel}; the JRC-Acquis Communautaire corpus (\domain{law}) \citep{Steinberger06acquis}; documentations for KDE, Ubuntu, GNOME and PHP from the Opus collection \citep{Tiedemann09news}, merged in a \domain{it}-domain; TedTalks (\domain{talk}) \citep{Cettolo12wit}, and the Koran (\domain{rel}). Complementary experiments also use v12 of the News Commentary corpus (\domain{news}). Most corpora are available from the Opus website.\footnote{\url{http://opus.nlpl.eu}} These corpora were deduplicated and tokenized with in-house tools; statistics are in Table~\ref{tab:Corpora}. To reduce the number of types and build open-vocabulary systems, we use Byte-Pair Encoding \citep{Sennrich16BPE} with 30,000 merge operations on a corpus containing all sentences in both languages.\fyDone{Add \# number of tokens, also specificity ?}%

We randomly select in each corpus a development and a test set of 1,000 lines and keep the rest for training. Validation sets are used to chose the best model according to the average BLEU score \citep{Papineni02bleu}.\footnote{We use truecasing and \texttt{sacrebleu}\citep{Post18call}.}\fyDone{A word about meta-parameter settings} Significance testing is performed using bootstrap resampling \citep{Koehn04statistical}, implemented in compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \citep{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.\fyDone{Fix correct p value}

@@

\begin{itemize}
\itemsep0em 
\item Generic models trained with various predefined mixtures of the training data taking the form:
\begin{align} \label{mixture:trn}
\lambda_{\alpha}(d) = \frac{q_d^{\alpha}}{\displaystyle{\mathop{\sum}_{d=1}^{n_d}q_d^{\alpha}}} &&
q_d = \frac{\mid N^{s}_d \mid}{\displaystyle{N^{s}}} % \mathop{\sum}_{i=1}^K\mid D_i \mid}}
\end{align} \setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt} 
with $\alpha \in [0,0.25,0.5,0.75,1.0]$. These systems are denoted \system{Mixed-$\alpha$} below. \system{Mixed-$0$} uses a uniform domain distribution, \system{Mixed-$1.0$} uses the observed domain distribution.
\item fine-tuned models \citep{Luong15stanford,Freitag16fast}, based on the \system{Mixed-$1.0$} system, further trained on each domain for at most 50~000 iterations, with early stopping when the dev BLEU stops increasing for 5 successive iterations.\fyDone{for ?? iterations} The full fine-tuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems, each adapted for one domain, with no parameter sharing across domains.
\item systems trained with fixed data mixtures corresponding to $\lambda^l \in \big[ \lambda_0, \lambda_{0.25}, \lambda_{0.5}, \lambda_{0.75}, \lambda_{1.0}\big]$; these are used in the multi-domain experiments of Section~\ref{ssec:mda};
\item  our own implementations of recent dynamic sampling proposals from the literature: Curriculum Learning (CL) of \citet{Zhang19curriculum} and Differential Data Selection (DDS) of \citet{Wang20balancing} (see details below);
\end{itemize}

All models use embeddings and hidden layers of dimension~512. Transformer models contain 8~attention heads in each of the 6+6 layers; the inner feedforward layer contains 2048 cells. Training uses batches of~12,288 tokens, Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$, Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ in all layers. We train all systems with 200k iterations.

\subsection{CL and DDS's re-implementation}\fyDone{Right place for this ?}
We re-implement DDS in Tensorflow without any change in the choices of parameterization and hyper-parameters compared to the original code of \citet{Wang20balancing}.\footnote{\url{https://github.com/cindyxinyiwang/multiDDS}}

We also re-implement the approach of \citet{Zhang19curriculum} according to the authors' description of the algorithm. For each domain adaptation experiment, we combine the training data of all other domains into one corpus, then compute the cross-entropy difference score of each source sentence of this combined dataset. We then sort and split the corpus into 9 shards and execute curriculum learning with 10 shards, using the in-domain corpus as the first shard.

@@

In our work, we parameterize the distribution $\lambda^l$ as follows (with $\beta=2$ in all experiments):\fyFuture{Explain why}
\begin{equation}
\lambda
^l(d;\vpsi) = \frac{\vpsi[d]^\beta}{\sum_i \vpsi[i]^\beta}. \nonumber
\end{equation}

Additional choices for the hyper-parameters of our method include the number of simulation steps $k=10$ and the learning rate $\mathbf{lr}_{data}=0.001$. We update the sampling distribution via 100 gradient descent iterations for almost all experimental settings except that for adaptation with automatic clusters (Section~\ref{ssec:clda}), where we use 20~gradient descent iterations to avoid converging to degenerate distributions.\fyFuture{Why? computation?} We split the training into 100 short sessions that last 2000 training steps each. The choice of those hyper-parameters is mostly heuristic except for the learning rate $\mathbf{lr}_{data}$ which is optimized via grid search over a range of values $[0.001,0.0025,0.005]$.

@@

We now compare the best MDAC system (using $\vlambda_{t=0} = \vlambda_0$) to full fine-tuning. According to Table~\ref{tab:da}, fine-tuning is better for large domains such as \domain{med} and \domain{law}, while MDAC outperforms fine-tuning by approximately 1.2 BLEU for \domain{bank} and 1.0 BLEU for \domain{rel}. This indicates that for small domains, out-of-domain data helps improve the generalization and that MDAC is able to exploit this advantage by balancing the in-domain and the out-of-domain training data instead of edging out the out-of-domain training data as in fine-tuning. The results for DDS display similar trends but are always outperformed by MDAC. The behavior of CL, which does only well the large domain \domain{med} lag somewhat behind.

@@

A second observation is that DDS is again outperformed by MDAC by a significant margin of 1.5 BLEU on average; the only domain where DDS does (much) better is \domain{med}. Figure~\ref{fig:sampling}, where we plot the evolution of the training mixture in the course of training sessions, helps understand the difference between the two methods. For DDS (Figure~\ref{fig:DDS}), the proportion of 6 domains quickly converges towards a bi-domain mode in which only \domain{med} and \domain{rel} have significant probability -- hence the good performance on the former domain. In contrast, the proportion of 6~domains computed by MDAC evolves more smoothly; small domains such as \domain{bank}, \domain{it}, \domain{talk} and \domain{rel} receive a larger proportion of training data in the early stages; their weights then slowly decrease as larger domains such as \domain{med} and \domain{law} increase their share. This, however, only happens at the end of the training, when the NMT models might have already been close to their optimal performance for the small domains.

@@

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*{10}{r|}} \cline{1-2} \cline{4-11}
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{news}}& \hfill &domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean}  \\ 
\cline{1-2} \cline{4-11}
    \multicolumn{2}{|c|}{\sl Unseen domain} & &\multicolumn{8}{c|}{\sl Training with 30 clusters} \\ 
\cline{1-2} \cline{4-11}
    \system{Mixed-0}      & 25.7 & &\system{DDS($\vlambda^*, \vlambda_d$)}&38.3&60.1&50.3&35.8&49.1&90.1&53.9\\
    \system{Mixed-0.25} & 25.8 & &\system{MDAC($\vlambda^*, \vlambda_d$)}&39.2$^*$&61.6$^*$&52.0$^*$&38.2$^*$&49.1&89.7&55.0$^*$\\ \cline{4-11}
    \system{Mixed-0.5}   &26.5\\
    \system{Mixed-0.75} &26.8\\
    \system{Mixed-1} &26.9 \\
    \cline{1-2}
     \system{DDS($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \system{MDAC($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \cline{1-2}
  \end{tabular}
  \caption{Few-shot adaptation (left) and unsupervised adaptation (right). For a given line, each column correspond to one distinct system. ($^*$) MDAC is significantly better than DDS.}
  \label{tab:unsupervised-da}
\end{table*}

@@

\subsection{Automatic clustering}\label{ssec:clda}
The right part of Table~\ref{tab:unsupervised-da} reports the performance of NMT systems adapted to each domain. In comparison to Section~\ref{ssec:da}, the training data is distributed in 30 automatic clusters instead of the 6 original domains. Splitting the train data into small groups provides the learner with extra degrees of freedom when selecting the best distribution. However, as these clusters are built automatically, they are noisier in nature. According to the results in Table~\ref{tab:unsupervised-da}, this scenario is hard both for DDS and MDAC, which perform much worse than for the supervised DA setting. This again signals the importance of initialization: analyzing the clustering, we find that the data for \domain{rel} mostly correspond to one single cluster. In using a uniform initialization, this cluster starts with a very small weight and never succeeds in yielding the (good) performance observed in the DA setting.

\section{Related Work \label{sec:related}}

>>>>

This problem is often approached by \emph{static} instance selection or re-weighting strategies, where the available training data is used in proportion to its relevance for the test conditions \citep{Moore10selection,Axelrod11domain}. Finding the optimal balance of training data is, however, a challenging task due, for instance, to the similarity between domains/languages, but also due to regularization effects of out-of-domain data \citep{Miceli-barone17regularization}. It may also be suboptimal, as some target domains or languages might be easier to train than others. Finally, improving the performance of the MT system in one domain will often hurt that of another \citep{Vanderwees17dynamic, Britz17mixing}, and improving model generalization across all domains \citep{koehn18findings} may not achieve optimally for any particular domain.

Several recent proposals
% \citep{Vanderwees17dynamic,Graves17automated,platanios19competence,Zhang19curriculum,Kumar19reinforcement,Wang20learning-multi,Wang20balancing,Wang20learning-multi}
have explored ways to instead consider \emph{dynamic} data selection and sampling strategies that surpass static strategies. Notably, \citet{Vanderwees17dynamic,Zhang19curriculum} construct a static curriculum, while \citet{Graves17automated,Platanios19competence,Kumar19reinforcement,Wang20learning-multi,Wang20balancing} build curricula that automatically adapt to the training data.

@@

The main challenge is then to make the best of this heterogeneous data, with the aim to achieve the optimal performance for the intended test conditions. These might correspond to data from just one of the training domains, as in standard supervised (multi-source) domain adaptation; a more difficult case is when the test data is from one domain unseen in training (unsupervised domain adaptation); in multi-domain adaptation finally, the test distribution is itself a mixture of domains, some of which may also be observed in training.  Without loss of generality, one may then assume that the test distribution takes the form $\mathcal{D}^{t}(x) = \sum_d \lambda^{t}(d) \mathcal{D}_d(x)$ - with only one non-null  component in the case of pure domain adaptation. These settings are illustrated on Figure~\ref{fig:mdmt-lambdas}.
\begin{figure}[h]
  \centering
  \includegraphics[width=0.48\textwidth]{mdmt-lambdas}
  \caption{Training and testing with distribution mismatch. We consider just three domains, and represent vectors of mixture weights $\vlambda^{s}$ and $\vlambda^{t}$ in the 3-dimensional simplex. Training with weights in (a) and testing with weights in (c) is supervised multi-source domain adaptation to domain~2 ($d_2$), while (b)-(c) is the unsupervised version, with no training data from $d_2$; training with weights in (a) and testing with weights in (d) is multi-domain learning, also illustrated with configurations (a)-(e) (training domain $d_1$ is not seen in test), and (b)-(d)  (test domain $d_2$ is unseen in training).}\label{fig:mdmt-lambdas}
\end{figure}

@@

\section{Experimental settings} \label{sec:exp}
\subsection{Data and metrics \label{ssec:corpora}}
We experiment with translation from English into French and use texts initially originating from 6~domains, corresponding to the following data sources: the UFAL Medical corpus V1.0 (\domain{med})\footnote{\url{https://ufal.mff.cuni.cz/ufal_medical_corpus}. We only use the in-domain (medical) subcorpora: PATR, EMEA, CESTA, ECDC.}; the European Central Bank corpus (\domain{bank}) \citep{Tiedemann12parallel}; the JRC-Acquis Communautaire corpus (\domain{law}) \citep{Steinberger06acquis}; documentations for KDE, Ubuntu, GNOME and PHP from the Opus collection \citep{Tiedemann09news}, merged in a \domain{it}-domain; TedTalks (\domain{talk}) \citep{Cettolo12wit}, and the Koran (\domain{rel}). Complementary experiments also use v12 of the News Commentary corpus (\domain{news}). Most corpora are available from the Opus website.\footnote{\url{http://opus.nlpl.eu}} These corpora were deduplicated and tokenized with in-house tools; statistics are in Table~\ref{tab:Corpora}. To reduce the number of types and build open-vocabulary systems, we use Byte-Pair Encoding \citep{Sennrich16BPE} with 30,000 merge operations on a corpus containing all sentences in both languages.\fyDone{Add \# number of tokens, also specificity ?}%
%
We randomly select in each corpus a development and a test set of 1,000 lines and keep the rest for training. Validation sets are used to chose the best model according to the average BLEU score \citep{Papineni02bleu}.\footnote{We use truecasing and \texttt{sacrebleu}\citep{Post18call}.}\fyDone{A word about meta-parameter settings} Significance testing is performed using bootstrap resampling \citep{Koehn04statistical}, implemented in compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \citep{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.\fyDone{Fix correct p value}

@@

\begin{itemize}
\itemsep0em 
\item Generic models trained with predefined mixtures of the training data taking the form:
\begin{align} \label{mixture:trn}
\lambda_{\alpha}(d) = \frac{q_d^{\alpha}}{\displaystyle{\mathop{\sum}_{d=1}^{n_d}q_d^{\alpha}}} &&
q_d = \frac{\mid N^{s}_d \mid}{\displaystyle{N^{s}}} % \mathop{\sum}_{i=1}^K\mid D_i \mid}}
\end{align}
%\setlength{\abovedisplayskip}{2pt}
% \setlength{\belowdisplayskip}{2pt} 
with $\alpha \in \{0,0.25,0.5,0.75,1.0\}$. We denote these as \system{Mixed-$\alpha$} below. \system{Mixed-$0$} uses a uniform distribution, \system{Mixed-$1.0$} the empirical domain distribution.
\item fine-tuned models \citep{Luong15stanford,Freitag16fast}, based on the \system{Mixed-$1.0$} system, further trained on each domain for at most 50~000 iterations, with early stopping when the dev BLEU stops increasing for 5 successive iterations.\fyDone{for ?? iterations} The full fine-tuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems, each adapted for one domain, with no parameter sharing across domains.
\item systems trained with fixed data mixtures corresponding to $\lambda^l \in \big[ \lambda_0, \lambda_{0.25}, \lambda_{0.5}, \lambda_{0.75}, \lambda_{1.0}\big]$; these are used in the multi-domain experiments of Section~\ref{ssec:mda};
\item  our own implementations of recent dynamic sampling proposals from the literature: Curriculum Learning (CL) of \citet{Zhang19curriculum} and Differential Data Selection (DDS) of \citet{Wang20balancing} (see details below);
\end{itemize}

All models use embeddings and hidden layers of dimension~512. Transformer models contain 8~attention heads in each of the 6+6 layers; the inner feedforward layer contains 2048 cells. Training lasts for 200K iterations, with batches of~12,288 tokens, Adam with parameters $\beta_1=0.9$, $\beta_2= 0.98$, Noam decay ($warmup\_steps=4000$), and a dropout rate of $0.1$ in all layers.

\subsection{CL and DDS's re-implementation}\fyDone{Right place for this ?}
We re-implement DDS in Tensorflow without any change in the choices of parameterization and hyper-parameters compared to the original code of \citet{Wang20balancing}.\footnote{\url{https://github.com/cindyxinyiwang/multiDDS}}
% 
We also re-implement the approach of \citet{Zhang19curriculum} according to the authors' description. For each domain adaptation experiment, we combine the training data of all other domains into one corpus then compute the cross-entropy difference score of each source sentence of this combined dataset. We then sort and split the corpus into 9 shards and execute curriculum learning with 10 shards, using the in-domain corpus as the first shard.

@@

In our work, we parameterize the distribution $\vlambda^l$ as follows (with $\beta=2$ in all experiments):\fyDone{Explain why}
\begin{equation}
\lambda^l(d;\vpsi) = \frac{\vpsi[d]^\beta}{\sum_i \vpsi[i]^\beta}. \nonumber
\end{equation}
This parameterization avoids the ``rich-get-richer'' effect that we observe when using $\vlambda(\vpsi) = \operatorname{softmax}(\vpsi)$, which yields gradients wrt. $\lambda_d$ to be proportional to $\lambda_d$ (see also Figure~\ref{fig:sampling}). Additional settings for the hyper-parameters of our method include the number of simulation steps $k=10$ and the learning rate $\mathbf{lr}_{data}=0.001$. We update the sampling distribution via 100 gradient descent iterations for almost all experimental settings except that for adaptation with automatic clusters (Section~\ref{ssec:clda}), where we use 20~gradient descent iterations to avoid converging to degenerate distributions.\fyFuture{Why? computation?} We split the training into 100 short sessions that last 2000 training steps each. The choice of those hyper-parameters is mostly heuristic except for the learning rate $\mathbf{lr}_{data}$ which is optimized via grid search over a set of values $\{0.001,0.0025,0.005\}$.

@@

We now compare the best MDAC system (using $\vlambda_{t=0} = \vlambda_0$) to full fine-tuning. According to Table~\ref{tab:da}, fine-tuning is better for large domains such as \domain{med} and \domain{law}, while MDAC outperforms fine-tuning by approximately 1.2 BLEU for \domain{bank} and 1.0 BLEU for \domain{rel}. This indicates that for small domains, out-of-domain data helps improve the generalization and that MDAC is able to exploit both the in-domain and the out-of-domain training data instead of edging out the out-of-domain training data as in fine-tuning. Results for DDS display similar trends but are always outperformed by MDAC. The behavior of CL, which does only well the large domain \domain{med} lag somewhat behind.

@@

A second observation is that DDS is again outperformed by MDAC by a significant margin of 1.5 BLEU on average; the only domain where DDS does (much) better is \domain{med}. Figure~\ref{fig:sampling}, where we plot the evolution of the training mixture in the course of training sessions, helps understand the difference between the two methods. For DDS (Figure~\ref{fig:DDS}), the sampling distribution quickly converges towards a bi-domain mode in which only \domain{med} and \domain{rel} have significant probability -- hence the good performance on the former domain. In contrast, the distribution computed by MDAC evolves more smoothly; small domains such as \domain{bank}, \domain{it}, \domain{talk} and \domain{rel} receive a larger proportion of training data in the early stages; their weights then slowly decrease as larger domains such as \domain{med} and \domain{law} increase their share. This, however, only happens at the end of the training, when the NMT models might have already been close to their optimal performance for the small domains.

@@

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*{10}{r|}} \cline{1-2} \cline{4-11}
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{news}}& \hfill &domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean}  \\ 
\cline{1-2} \cline{4-11}
    \multicolumn{2}{|c|}{\sl Unseen domain} & &\multicolumn{8}{c|}{\sl Training with 30 clusters} \\ 
\cline{1-2} \cline{4-11}
    \system{Mixed-0}      & 25.7 & &\system{DDS($\vlambda^*, \vlambda_d$)}&38.3&60.1&50.3&35.8&49.1&90.1&53.9\\
    \system{Mixed-0.25} & 25.8 & &\system{MDAC($\vlambda^*, \vlambda_d$)}&39.2$^*$&61.6$^*$&52.0$^*$&38.2$^*$&49.1&89.7&55.0$^*$\\ \cline{4-11}
    \system{Mixed-0.5}   &26.5\\
    \system{Mixed-0.75} &26.8\\
    \system{Mixed-1} &26.9 \\
    \cline{1-2}
     \system{DDS($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \system{MDAC($\vlambda_0, \vlambda_{news}$)} &26.3 \\
     \cline{1-2}
  \end{tabular}
  \caption{Few-shot adaptation (left) and unsupervised adaptation (right). For a given line, each column corresponds to one distinct system. ($^*$) MDAC is significantly better than DDS.}
  \label{tab:unsupervised-da}
\end{table*}

@@

\subsection{Automatic clustering}\label{ssec:clda}
The right part of Table~\ref{tab:unsupervised-da} reports the performance of NMT systems adapted to each domain. In comparison to Section~\ref{ssec:da}, the training data is distributed in 30 automatic clusters instead of the 6 original domains. Splitting the train data into small groups provides the learner with extra degrees of freedom when selecting the best distribution. However, as these clusters are built automatically, they are noisier in nature. According to the results in Table~\ref{tab:unsupervised-da}, this scenario is hard both for DDS and MDAC, which perform much worse than for the supervised DA setting. This again signals the importance of initialization: analyzing the clustering, we find that the data for \domain{rel} mostly correspond to one single cluster. When using a uniform initialization, this cluster starts with a very small weight and never succeeds in yielding the (good) performance observed in the DA setting.
s
\section{Related Work \label{sec:related}}
